---
title: "ANOVAs_Glasser_Revision"
author: "Arielle Keller"
date: "8/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=250)
library(tidyr)
library(dplyr)
library(ggplot2)
library(lsr)
```

# ANOVA on residual correlations. This is a 3-way repeated-measure ANOVA with "Lobe" (Frontal, Parietal, Temporal, Occipital), "Hemisphere" (left vs right) and "AttendIgnore" (attend preferred category, ignore preferred category). In all cases, I am collapsing across the 4 object categories/VTC regions (faces, houses, bodies, words).


```{r, include=FALSE}
data <- read.csv("data_residual_correlations.csv")
data$Subject = as.factor(rep(c(1:21),684))
data$Hemisphere = as.factor(data$Hemisphere)
data$Lobe = as.factor(data$Lobe)
data$AttendIgnore = as.factor(data$AttendIgnore)
data$RegionID = as.factor(data$RegionID)
```


## Residual Correlations ANOVA results with interactions:
```{r}
summary(aov(ResidualCorrelations ~ Lobe+AttendIgnore+Hemisphere+Lobe:AttendIgnore+Lobe:Hemisphere+AttendIgnore:Hemisphere+Lobe:Hemisphere:AttendIgnore+Error(Subject/(Lobe*Hemisphere*AttendIgnore)), data=data))
```


## Make Figure showing results
```{r}
df.summary <- data %>%
     group_by(AttendIgnore,Lobe,Hemisphere) %>%
     summarise(
         se = sd(ResidualCorrelations, na.rm = TRUE)/sqrt(length(ResidualCorrelations)),
         ResidualCorrelations = mean(ResidualCorrelations))


df.summary$Lobe <- c(4,4,3,3,2,2,1,1,4,4,3,3,2,2,1,1) # re-order the lobes for the plot
ggplot(df.summary, aes(x=factor(Lobe,labels=c("Occipital","Temporal","Parietal","Frontal")),y=ResidualCorrelations,fill=as.factor(interaction(AttendIgnore,Lobe)))) +
  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Lobe") + ylab("Residual Correlations") + geom_errorbar(aes(ymin=ResidualCorrelations-se, ymax=ResidualCorrelations+se), width=.2,
                 position=position_dodge(.9)) + scale_fill_manual(name="Condition",
                         values = c(rgb(103/255,129/255,186/255),rgb(70/255,179/255,143/255),rgb(180/255,92/255,111/255),rgb(246/255,125/255,73/255),rgb(205/255,213/255,228/255),rgb(185/255,220/255,200/255),rgb(242/255,215/255,222/255),rgb(248/255,215/255,178/255)),
                         breaks=c("1.1", "1.2", "1.3", "1.4", "2.1", "2.2", "2.3", "2.4"),
                         labels=c("Attended","Attended","Attended","Attended","Ignored","Ignored", "Ignored","Ignored"))+ facet_wrap(~ factor(Hemisphere,labels=c("Left Hemisphere","Right Hemisphere")),scales='free_y') + geom_ribbon(aes(x=c(0.5,0.5,0.5,0.5,0.5,0.5,4.5,4.5,4.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5),ymin = -0.02, ymax = 0.04),fill="grey70",alpha=0.5)+ geom_segment(aes(x=0.5,xend=4.58,y=0.01,yend=0.01),linetype="solid") +coord_cartesian(ylim=c(-0.1,0.4))
```


# ANOVA on classification accuracy. This is a 3-way repeated-measure ANOVA with "Lobe" (Frontal, Parietal, Temporal, Occipital), "Hemisphere" (left vs right) and "AttendIgnore" (attend preferred category, ignore preferred category). In all cases, I am collapsing across the 4 object categories/VTC regions (faces, houses, bodies, words).


```{r, include=FALSE}
data <- read.csv("data_classification_accuracy.csv")
data$Subject = as.factor(rep(c(1:21),684))
data$Hemisphere = as.factor(data$Hemisphere)
data$Lobe = as.factor(data$Lobe)
data$AttendIgnore = as.factor(data$AttendIgnore)
data$RegionID = as.factor(data$RegionID)
```


## Classification Accuracy ANOVA results with interactions:
```{r}
summary(aov(ClassificationAccuracy ~ Lobe+AttendIgnore+Hemisphere+Lobe:AttendIgnore+Lobe:Hemisphere+AttendIgnore:Hemisphere+Lobe:Hemisphere:AttendIgnore+Error(Subject/(AttendIgnore*Hemisphere*Lobe)), data=data))
```


## Make Figure showing results
```{r}
df.summary <- data %>%
     group_by(AttendIgnore,Lobe,Hemisphere) %>%
     summarise(
         se = sd(ClassificationAccuracy, na.rm = TRUE)/sqrt(length(ClassificationAccuracy)),
         ClassificationAccuracy = mean(ClassificationAccuracy))


df.summary$Lobe <- c(4,4,3,3,2,2,1,1,4,4,3,3,2,2,1,1)
ggplot(df.summary, aes(x=factor(Lobe,labels=c("Occipital","Temporal","Parietal","Frontal")),y=ClassificationAccuracy,fill=as.factor(interaction(AttendIgnore,Lobe)))) +
  geom_bar(stat="identity",position="dodge") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +xlab("Lobe") + ylab("Classification Accuracy") + geom_errorbar(aes(ymin=ClassificationAccuracy-se, ymax=ClassificationAccuracy+se), width=.2,
                 position=position_dodge(.9)) + scale_fill_manual(name="Condition",
                         values = c(rgb(103/255,129/255,186/255),rgb(70/255,179/255,143/255),rgb(180/255,92/255,111/255),rgb(246/255,125/255,73/255),rgb(205/255,213/255,228/255),rgb(185/255,220/255,200/255),rgb(242/255,215/255,222/255),rgb(248/255,215/255,178/255)),
                         breaks=c("1.1", "1.2", "1.3", "1.4", "2.1", "2.2", "2.3", "2.4"),
                         labels=c("Attended","Attended","Attended","Attended","Ignored","Ignored", "Ignored","Ignored")) + facet_wrap(~ factor(Hemisphere,labels=c("Left Hemisphere","Right Hemisphere"))) + geom_ribbon(aes(x=c(0.5,0.5,0.5,0.5,0.5,0.5,4.5,4.5,4.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5),ymin = 0.177, ymax = 0.223),fill="grey70",alpha=0.5)+ geom_segment(aes(x=0.5,xend=4.58,y=0.2,yend=0.2),linetype="solid") +coord_cartesian(ylim=c(0,0.75))
```


